Figures main manuscript

### 2020-03-30 code/05_figures-and-correlations.rmd
Made legend wider in Fig 1 for better clarity

#combined line plot gives good overview.
ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type, linetype = effect_type)) +
  geom_line(alpha = 0.6) +
  theme_bw() +
  scale_x_continuous(name = expression(paste("Between studies standard deviation ", tau)),
                     minor_breaks = NULL) +
  scale_y_continuous(name = expression(paste("Average ", italic(I)^2," index", sep = "")),
                     minor_breaks = NULL) +
  scale_linetype_manual(name = "Effect type", 
                        values = c( "dotdash", "dotted", "solid", "dashed"),
                        breaks = c("Fisher's z", "Cohen's q", "MD", "SMD"),
                        labels = c(expression(paste("Fisher's ", italic(z))),
                                   expression(paste("Cohen's ", italic(q))),
                                   expression(paste(italic(MD))),
                                   expression(paste(italic(SMD))))) + 
  scale_color_brewer(name = "Effect type", 
                     palette = "Dark2", 
                     breaks = c("Fisher's z", "Cohen's q", "MD", "SMD"),
                     labels = c(expression(paste("Fisher's ", italic(z))),
                                   expression(paste("Cohen's ", italic(q))),
                                   expression(paste(italic(MD))),
                                   expression(paste(italic(SMD))))) +
  coord_cartesian(ylim = c(0, 100)) +
  theme(legend.position = c(0.8, 0.4),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  guides(color = guide_legend(override.aes = list(size = 1.2)))

>>>>

#combined line plot gives good overview.
ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type, linetype = effect_type)) +
  geom_line(alpha = 0.6) +
  theme_bw() +
  scale_x_continuous(name = expression(paste("Between studies standard deviation ", tau)),
                     minor_breaks = NULL) +
  scale_y_continuous(name = expression(paste("Average ", italic(I)^2," index", sep = "")),
                     minor_breaks = NULL) +
  scale_linetype_manual(name = "Effect type", 
                        values = c( "dotdash", "dotted", "solid", "dashed"),
                        breaks = c("Fisher's z", "Cohen's q", "MD", "SMD"),
                        labels = c(expression(paste("Fisher's ", italic(z))),
                                   expression(paste("Cohen's ", italic(q))),
                                   expression(paste(italic(MD))),
                                   expression(paste(italic(SMD))))) + 
  scale_color_brewer(name = "Effect type", 
                     palette = "Dark2", 
                     breaks = c("Fisher's z", "Cohen's q", "MD", "SMD"),
                     labels = c(expression(paste("Fisher's ", italic(z))),
                                   expression(paste("Cohen's ", italic(q))),
                                   expression(paste(italic(MD))),
                                   expression(paste(italic(SMD))))) +
  coord_cartesian(ylim = c(0, 100)) +
  theme(legend.position = c(0.8, 0.4),
        legend.background = element_rect(linetype = "solid", color = "black"),
        legend.key.width = unit(0.9, "cm")) +
  guides(color = guide_legend(override.aes = list(size = 0.85)))
